Hydras \& Co.

### 2022-03-09 doc/gaia-chapter.tex
Minor corrections

The library \href{../theories/html/gaia_hydras.GPaths.html}%
{\texttt{gaia\_hydras.GPaths}} imports definitions and lemmas from
\href{../theories/html/hydras.Epsilon0.Paths.html}%
{\texttt{hydras.Epsilon0.Paths}}.

Please refer to Sect.~\ref{sect:pathes-intro} for a descrition of that library.

@@

\subsection{A family of rapidly growing functions}

@@

>>>>

The library \href{../theories/html/gaia_hydras.GPaths.html}%
{\texttt{gaia\_hydras.GPaths}} imports definitions and lemmas from
\href{../theories/html/hydras.Epsilon0.Paths.html}%
{\texttt{hydras.Epsilon0.Paths}} (described in Sect.~\ref{sect:pathes-intro}).

@@

\subsection{A family of rapidly growing functions
(Library \texttt{GF\_alpha})}

@@

From~\href{../theories/html/gaia_hydras.G~F_alpha.html}%
{\texttt{gaia\_hydras.GF\_alpha}}.
